---
title: "Title of the report"
subtitle: "Subtitle of the report"
author: "Author Name"
date: "Date"
output: 
    pagedreport::paged_grid:
      logo: "https://mk0rfortheresto0o08q.kinstacdn.com/wp-content/uploads/2020/08/rru-logo-blue.svg"
knit: pagedown::chrome_print
main-color: "#6cabdd"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

# This is part 1 {-}

```{r}
up <- function(){
	fontawesome::fa(name = "arrow-up", fill = "red")
}

down <- function(){
	fontawesome::fa(name = "arrow-down", fill = "green")
}
```




## Second level {-}

Some general text here to set the context.

<center>
|Test|Direction|
|---|----------|
|Cases| `r up()`|
Table: A Nice table

</center>

```{r}
gt::gt(head(mtcars,5), caption = "Another table")
```

```{r}

dat_test <- tibble::tibble(
	mesure = rpois(2, 100),
	direction = list(up(), down())
)
library(dplyr)
library(gt)
gt::gt(dat_test) %>% 
	text_transform(locations = cells_body(columns = vars(direction)),
								 fn = function(x){
								 	x
								 })

```

<svg aria-hidden="true" role="img" viewBox="0 0 448 512" style="height:1em;width:0.88em;vertical-align:-0.125em;margin-left:auto;margin-right:auto;font-size:inherit;fill:red;overflow:visible;position:relative;"><path d="M34.9 289.5l-22.2-22.2c-9.4-9.4-9.4-24.6 0-33.9L207 39c9.4-9.4 24.6-9.4 33.9 0l194.3 194.3c9.4 9.4 9.4 24.6 0 33.9L413 289.4c-9.5 9.5-25 9.3-34.3-.4L264 168.6V456c0 13.3-10.7 24-24 24h-32c-13.3 0-24-10.7-24-24V168.6L69.2 289.1c-9.3 9.8-24.8 10-34.3.4z"/></svg>


## Second level {-}

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message! This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.


+ item 1
+ item 2
+ item 3

1. numbered 1
2. numbered 2
3. numbered 3


## Second level {-}

Finally, be sure to remove this message!
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

# And now part 2 {-}

This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

## Second level {-}

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
